---
title: "R Homework"
author: "Jeho Park"
date: "11/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homework Assignment

### The following R code chunk runs the code within the chunk block and displays the result beneath the chunk.

```{r cars}
summary(cars)
```

#### To learn more about R Markdown, check out the R Markdown tutorial at https://rmarkdown.rstudio.com/lesson-1.html 

### (1) Using cars dataset, create a vector 'stop_mean' that contains mean stopping distance and display the result.
```{r stop_mean_chunk}
# Type your answer below
stop_mean <- mean(cars$dist)
```

### (2) Create a matrix 'cars_mat' by converting the cars dataset (which is a data frame) and diplay its type.
```{r cars_mat_chunk}
# Type your answer below

```
### The following chunk will load 'hflights' datasets. If it's not already installed, it will install the package
#### (Do not change the chunk below)
```{r hflight-install}
if(!require(hflights)) install.packages("hflights",repos = "http://cran.us.r-project.org")
```

### (3) Diplay the stucture of the hflights datasets
```{r hfligt_structure}
# Type your answer below

```

### (4) Using hflights datasets, create a variable called 'x' that contains the mean flight arrival delay and display the value  (which should be 7.094334) 
#### Hint: There are missing values. So the question is how to exclude those missing values from the data.

```{r}
# Type your answer below

```

_[Source] SCF/D-Lab R bootcamp at UC Berkeley_
